Intelligent Quadcopter for IARC 2018

### 2018-06-01 IARC_Paper_2018/Paper.tex
Small spelling standarizations

	\begin{figure}[!htbp]
	\begin{center}
	\begin{tikzpicture}[node distance = 1.5cm and 8cm, auto]
		% Place nodes
		\node [block] (battery) {Battery};
		\node [block, below of=battery] (siphon) {Power siphon};
		\node [block, below of=siphon] (Pixhawk) {Pixhawk};
		\node [block, below right of=battery, xshift=3cm, align=center] (PDB) {Power Distribution \\ Board};
		\node [block, below left of=battery, xshift=-3cm, yshift=-.7cm] (Jetson) {Nvidia Jetson TX2s};
		\node [block, right of=Pixhawk, xshift=2.6cm] (ESCs) {ESCs};
		\node [block, below right of=ESCs, xshift=.5cm] (Motors) {Motors};
		\node [block, below right of=Jetson] (Camera) {Cameras};
		\node [block, below left of=Jetson] (2dLidar) {2D LiDAR};
		\node [block, below right of=Pixhawk, yshift=-1cm] (Flow) {PX4FLOW};
		\node [block, below right of=Pixhawk, xshift=3.5cm, yshift=-1cm] (Spektrum) {Spektrum controller};
		\node [block, below left of=Pixhawk, xshift=-.5cm, yshift=-1cm] (LIDAR) {LIDAR};
		\node [block, below left of=Pixhawk, xshift=-3.5cm, yshift=-1cm] (Telemetry) {Ground Telemetry};
		% Draw edges
		\path [line] (battery) -- (siphon);
		\path [line] (siphon) -- (Pixhawk);
		\path [line] (battery) -- (PDB);
		\path [line] (PDB) -- (ESCs);
		\path [line] (battery) -- (Jetson);
		\path [line, dashed] (Camera) -- (Jetson);
		\path [line, dashed] (2dLidar) -- (Jetson);
		\path [line, dashed] (Flow) -- (Pixhawk);
		\path [line, dashed] (Jetson) -- (Pixhawk);
		\path [line, dashed] (LIDAR) -- (Pixhawk);
		\path [line, dashed] (Pixhawk) -- (Telemetry);
		\path [line, dashed] (Spektrum) -- (Pixhawk);
		\path [line, dashed] (Pixhawk) -- (ESCs);
		\path [line] (ESCs) -- (Motors);
	\end{tikzpicture}
	\caption*{Flowchart of quadcopter electronics \\ \tiny *Solid arrows indicate power while dashed lines indicate power+data}
	\end{center}
	\end{figure}

@@

	\subsection*{Guidance, Navigation, and Control}
		\subsubsection*{Stability Augmentation System}
			Our system builds off of the robust open source project Arducopter. Arducopter, runs on the Pixhawk, and controls the stability of the drone by taking in data from the IMU, compass, altitude LIDAR and the optical flow sensor. The Arducopter flight stack is maintained by hundreds of developers from around the world and the software is deployed on thousands of commercial and recreational drones. The vast community of developers and users ensures refined controls code with lots of features.

		\subsubsection*{Navigation}
			We have made slight modifications to the Arducopter firmware, which allow us to set the EKF origin. This has been done to allow our drone to navigate in GPS denied environments. For general waypoint navigation, the drone utilizes the Arducopter EKF that takes in data from the IMU, compass, altitude LIDAR and the optical flow sensor. The EKF position is then queried via mavros, so that our strategy code can use our position to make intelligent decisions. In addition, the strategy node takes in data from computer vision and 2d lidar. The strategy will determine a waypoint and mode, and the ros controls node will do a sanity check on the waypoint, then publish the waypoint until the drone has reached its destination. Over time, the EKF will have error in comparison to reality. To combat this, the control node will input a correction vector. This correction vector is formed from our computer vision algorithm that recognizes the absolute corners of the grid. This algorithm goes as follows. Gaussian blur, color threshold, erosion, dilation, Canny, Hough, line intersection, and non maximum suppression.

@@

		% \begin{figure}[!htbp]
		% 	\begin{center}
		% 		\begin{tikzpicture}[node distance = 3cm, auto]
		% 			% Place nodes
		% 			\node [block] (IMU) {IMU + Flow};
		% 			\node [block, below of=IMU] (Camera) {Camera};
		% 			\node [block, right of=IMU] (EKF) {EKF};
		% 			\node [block, below of=EKF] (Vision) {Vision};
		% 			\node [block, below right of=EKF] (Strategy) {Strategy};
		% 			\node [block, below right of=Strategy] (2DLIDAR) {2D LIDAR};
		% 			\node [block, right of=Strategy] (mavros) {mavros};
		% 			\node [block, right of=mavros] (Pixhawk) {Pixhawk};
		% 			\node [block, right of=Pixhawk] (Move) {Move};
		% 			% Draw edges
		% 			\path [line] (IMU) -- (EKF);
		% 			\path [line] (Camera) -- (Vision);
		% 			\path [line] (EKF) -- (Strategy);
		% 			\path [line] (Vision) -- (Strategy);
		% 			\path [line] (2DLIDAR) -- (Strategy);
		% 			\path [line] (2DLIDAR) -- (mavros);
		% 			\path [line] (Strategy) -- (mavros);
		% 			\path [line] (mavros) -- (Pixhawk);
		% 			\path [line] (Pixhawk) -- (Move);
		% 		\end{tikzpicture}
		% 		\caption*{Overview of control system}
		% 	\end{center}
		% \end{figure}

		\subsubsection*{Flight Termination System}
			Our drone houses a 40 amp brushless esc connected to a rc receiver, which acts as our kill switch. In the event of catastrophic failure the safety operator can send the kill signal, and all power will be cut to the drone's systems.

\section*{Payload}
	The Drone has been designed to carry all the necessary GNC sensors, 2d LIDAR, and array of cameras and 3 nvidia TX2 Jetsons. In addition the drone carries a telemetry radio, kill switch and rc receiver in order to carry out safe flight.
	\subsection*{Sensor Suite}
		\subsubsection*{GNC Sensors}
			The quadcopter uses eight sensors for flight control. The main sensors used for the navigation of the quadcopter are a downwards-facing 1-D LiDAR module, a PX4FLOW optical sensor, and the built-in sensors of our flight control board, the Pixhawk 2.

@@

\section*{Operations}
	\subsection*{Flight Preparations}
		\subsubsection*{Checklist}
			\begin{my_enumerate}
				\item Check battery voltage (12.0-12.6v) and insert
				\item Make sure LIDAR and PX4FLOW are not covered
				\item Make sure that ESCs are plugged in to the right pins
				\item Make sure prop guards are secure
				\item Make sure that the props are on in the correct direction (leading edge in)
				\item Make sure that the props are not upside down
				\item Make sure props are clear of any structures
				\item Make sure Kill Switch is in off position
				\item Power on controllers
				\item Make sure TELEM2 is unplugged
				\item Plug in power loop
				\item Turn Kill Switch to on position
				\item Make sure ground station has good telemetry
				\item Verify critical sensors are giving good data
				\item Plug in TELEM2
				\item SSH start/verify autonomous scripts are running
				\item Make sure everyone is clear of drone
				\item Verify mode switch in Stabilize
				\item Hold safety button
				\item Mode switch to Autonomous
			\end{my_enumerate}
	\subsection*{Man/Machine Interface}
		The drone has a DX7 RC controller interface for system checks and emergency situations. In addition, the flight controller can be monitored via a telemetry radio using Mission Planner. Our autonomous scripts must be initiated by an SSH connection to our Nvidia Jetsons.

>>>>

	\begin{figure}[!htbp]
	\begin{center}
	\begin{tikzpicture}[node distance = 1.5cm and 8cm, auto]
		% Place nodes
		\node [block] (battery) {Battery};
		\node [block, below of=battery] (siphon) {Power siphon};
		\node [block, below of=siphon] (Pixhawk) {Pixhawk};
		\node [block, below right of=battery, xshift=3cm, align=center] (PDB) {Power Distribution \\ Board};
		\node [block, below left of=battery, xshift=-3cm, yshift=-.7cm] (Jetson) {Nvidia Jetson TX2s};
		\node [block, right of=Pixhawk, xshift=2.6cm] (ESCs) {ESCs};
		\node [block, below right of=ESCs, xshift=.5cm] (Motors) {Motors};
		\node [block, below right of=Jetson] (Camera) {Cameras};
		\node [block, below left of=Jetson] (2dLidar) {2D LiDAR};
		\node [block, below right of=Pixhawk, yshift=-1cm] (Flow) {PX4FLOW};
		\node [block, below right of=Pixhawk, xshift=3.5cm, yshift=-1cm] (Spektrum) {Spektrum controller};
		\node [block, below left of=Pixhawk, xshift=-.5cm, yshift=-1cm] (LiDAR) {LiDAR};
		\node [block, below left of=Pixhawk, xshift=-3.5cm, yshift=-1cm] (Telemetry) {Ground Telemetry};
		% Draw edges
		\path [line] (battery) -- (siphon);
		\path [line] (siphon) -- (Pixhawk);
		\path [line] (battery) -- (PDB);
		\path [line] (PDB) -- (ESCs);
		\path [line] (battery) -- (Jetson);
		\path [line, dashed] (Camera) -- (Jetson);
		\path [line, dashed] (2dLidar) -- (Jetson);
		\path [line, dashed] (Flow) -- (Pixhawk);
		\path [line, dashed] (Jetson) -- (Pixhawk);
		\path [line, dashed] (LiDAR) -- (Pixhawk);
		\path [line, dashed] (Pixhawk) -- (Telemetry);
		\path [line, dashed] (Spektrum) -- (Pixhawk);
		\path [line, dashed] (Pixhawk) -- (ESCs);
		\path [line] (ESCs) -- (Motors);
	\end{tikzpicture}
	\caption*{Flowchart of quadcopter electronics \\ \tiny *Solid arrows indicate power while dashed lines indicate power+data}
	\end{center}
	\end{figure}

@@

	\subsection*{Guidance, Navigation, and Control}
		\subsubsection*{Stability Augmentation System}
			Our system builds off of the robust open source project Arducopter. Arducopter, runs on the Pixhawk, and controls the stability of the drone by taking in data from the IMU, compass, altitude LiDAR and the optical flow sensor. The Arducopter flight stack is maintained by hundreds of developers from around the world and the software is deployed on thousands of commercial and recreational drones. The vast community of developers and users ensures refined controls code with lots of features.

		\subsubsection*{Navigation}
			We have made slight modifications to the Arducopter firmware, which allow us to set the EKF origin. This has been done to allow our drone to navigate in GPS denied environments. For general waypoint navigation, the drone utilizes the Arducopter EKF that takes in data from the IMU, compass, altitude LiDAR and the optical flow sensor. The EKF position is then queried via mavros, so that our strategy code can use our position to make intelligent decisions. In addition, the strategy node takes in data from computer vision and 2d lidar. The strategy will determine a waypoint and mode, and the ros controls node will do a sanity check on the waypoint, then publish the waypoint until the drone has reached its destination. Over time, the EKF will have error in comparison to reality. To combat this, the control node will input a correction vector. This correction vector is formed from our computer vision algorithm that recognizes the absolute corners of the grid. This algorithm goes as follows. Gaussian blur, color threshold, erosion, dilation, Canny, Hough, line intersection, and non maximum suppression.

@@

		% \begin{figure}[!htbp]
		% 	\begin{center}
		% 		\begin{tikzpicture}[node distance = 3cm, auto]
		% 			% Place nodes
		% 			\node [block] (IMU) {IMU + Flow};
		% 			\node [block, below of=IMU] (Camera) {Camera};
		% 			\node [block, right of=IMU] (EKF) {EKF};
		% 			\node [block, below of=EKF] (Vision) {Vision};
		% 			\node [block, below right of=EKF] (Strategy) {Strategy};
		% 			\node [block, below right of=Strategy] (2DLiDAR) {2D LiDAR};
		% 			\node [block, right of=Strategy] (mavros) {mavros};
		% 			\node [block, right of=mavros] (Pixhawk) {Pixhawk};
		% 			\node [block, right of=Pixhawk] (Move) {Move};
		% 			% Draw edges
		% 			\path [line] (IMU) -- (EKF);
		% 			\path [line] (Camera) -- (Vision);
		% 			\path [line] (EKF) -- (Strategy);
		% 			\path [line] (Vision) -- (Strategy);
		% 			\path [line] (2DLiDAR) -- (Strategy);
		% 			\path [line] (2DLiDAR) -- (mavros);
		% 			\path [line] (Strategy) -- (mavros);
		% 			\path [line] (mavros) -- (Pixhawk);
		% 			\path [line] (Pixhawk) -- (Move);
		% 		\end{tikzpicture}
		% 		\caption*{Overview of control system}
		% 	\end{center}
		% \end{figure}

		\subsubsection*{Flight Termination System}
			Our drone houses a 40 [A] brushless ESC connected to a RC receiver, which acts as our kill switch. In the event of catastrophic failure the safety operator can send the kill signal, and all power will be cut to the drone's systems.

\section*{Payload}
	The drone has been designed to carry all the necessary GNC sensors, 2D LiDAR, and array of cameras and 3 Nvidia Jetson TX2s. In addition the drone carries a telemetry radio, kill switch, and RC receiver in order to carry out safe flight.
	\subsection*{Sensor Suite}
		\subsubsection*{GNC Sensors}
			The quadcopter uses eight sensors for flight control. The main sensors used for the navigation of the quadcopter are a downwards-facing 1D LiDAR module, a PX4FLOW optical sensor, and the built-in sensors of our flight control board, the Pixhawk 2.

@@

\section*{Operations}
	\subsection*{Flight Preparations}
		\subsubsection*{Checklist}
			\begin{my_enumerate}
				\item Check battery voltage (12.0-12.6v) and insert
				\item Make sure LiDAR and PX4FLOW are not covered
				\item Make sure that ESCs are plugged in to the right pins
				\item Make sure prop guards are secure
				\item Make sure that the props are on in the correct direction (leading edge in)
				\item Make sure that the props are not upside down
				\item Make sure props are clear of any structures
				\item Make sure Kill Switch is in off position
				\item Power on controllers
				\item Make sure TELEM2 is unplugged
				\item Plug in power loop
				\item Turn Kill Switch to on position
				\item Make sure ground station has good telemetry
				\item Verify critical sensors are giving good data
				\item Plug in TELEM2
				\item SSH start/verify autonomous scripts are running
				\item Make sure everyone is clear of drone
				\item Verify mode switch in Stabilize
				\item Hold safety button
				\item Mode switch to Autonomous
			\end{my_enumerate}
	\subsection*{Man/Machine Interface}
		The drone has a DX7 RC controller interface for system checks and emergency situations. In addition, the flight controller can be monitored via a telemetry radio using Mission Planner. Our autonomous scripts must be initiated by an SSH connection to our Nvidia Jetsons.
